---
title: "Vignette for codes used for the simulation study Alam and Staicu, 20xx"
format: gfm
---

This file illustrates how to use the codes in files *utilities_generate.R*, *utilities_main.R*, and *utilities_estimate.R* to reproduce the simulation study. 

- First, load all the functions in files *utilities_generate.R* and *utilities_main.R*
```{r}
source("utilities_generate.R")
source("utilities_main.R")
```

- Note that, all the functions in files *utilities_generate.R* and *utilities_main.R* are available in *sLFDA* package. It can be installed from github via
```{r}
#| eval: false
#| warning: false
#| message: false
devtools::install_github("https://github.com/msalam14/sLFDA")
```

- All the simulation results, except the quantile trajectory estimation via the proposed *sLFDA* approach, are obtained by excuting the codes written in *utilities_estimate.R* script.
```{r}
#| eval: false
source("utilities_estimate.R")
```

::: callout-tip
### Note
We perform the simulation on HPC; particularly, parallel jobs were run on distributed memory. To do so, we use the *Rmpi* package in the script *utilities_estimate.R*. For a given sample size and skewness type, this script will save $4$ files; in total $36$ files will be stored for $9$ scenarios ($3$ sample sizes and $3$ skewness scenarios)
:::

- The *R* script named as *utilities_results.R* contains all the necessary codes to summarize simulation results stored in the $36$ files by the script *utilities_estimate.R*. This script also generate the Tables provided in the original manuscript and supplementary material.

